\documentclass[margin,line]{resume}
\begin{document}
\vspace{10mm}\hspace{80mm}\name{\Large Christine Costales}
\begin{resume}




    %____________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}\vspace{1mm}

    \begin{tabular}{@{} l @{\hspace{45mm}} l @{\hspace {2mm}} l}
         555 West Madison Street Unit 3504 & Cell:  224-425-9596  \\
          Chicago, Illinois,  60661  & Email:  christine.costales@gmail.com       \\
    \end{tabular}
    %____________________________________________________________________________________
    % Objective
    \section{\mysidestyle Objective}

	To obtain an engaging position that will utilize my academic and applied experience in a challenging workplace that will provide room for professional and academic advancement.

%_____________________________________________________________________________
    %____________________________________________________________________________________
    % Education
%% TODO/Comments:
%  Update the dates to include the months for the Educaiton section.
%  it looks a smidge odd to have the GPA included for Daley, but not UIC.
%  Personal skills probably shouldn't be listed here, but all of these ``skills`` should be demonstrated by bullet points in your education/professional experience.  
	% ie.  dependable:  was responsible for a, b,c,d.  

    \section{\mysidestyle Education}

    {\bf University of Illinois at Chicago}, Chicago, Illinois\vspace{2mm}%
    \begin{list1}
    \item[] {\sl Bachelors in Computer Science}
    \begin{list2}
        \item Graduated:  December 2011
    \end{list2}
    \end{list1}




	\vspace{2mm}
    %____________________________________________________________________________________
    % Education

  \section{\mysidestyle Technical\\Skills}
    \begin{list2}
		\item {\sl Programming Languages:}  C++, Java, Smalltalk, Qt
		\item {\sl Operating Systems:}  Ubuntu Linux, Windows 7, Windows XP
        \item {\sl Programming Tools:} Visual Studio, Eclipse, gcc, gdb, make, request tracker, svn, git
    \end{list2}

    %____________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}
	\vspace{2mm}



    {\bf UIC Academic Computing and Communications Center}, Chicago, Illinois\\
    \vspace{1mm}{\sl Computer Consultant } \hfill {\bf August 2010 - August 2011}
    \begin{list2}
        \item Trained and supervised new student ACCC employees on proper procedures and tasks.
        \item Helped students, faculty, and staff with technical questions regarding account access, software troubleshooting, passwords and printing via phone, e-mail, and walk-in support.
        \item Improved the current ACCC workflow by extending the documentation knowledge base.  
    \end{list2}

    {\bf UIC Department of Computer Science}, Chicago, Illinois\\
    \vspace{1mm}{\sl ACCC Computer Specialist} \hfill {\bf February 2009 -- February 2010}
    

    \begin{list2}
        \item Responsible for the repair, maintenance of printers, computers, and projects in two Linux labs.
        \item Assisted students and staff with account related issues.
    \end{list2}



    {\bf Niro, Haller and Niro }, Chicago, Illinois\\
    \vspace{1mm}{\sl Junior Computer Consultant } \hfill {\bf January 2009 -- May 2009 }
    

    \begin{list2}
        \item Analyzed patented source code in order to better assist case lawyers with pending litigation.
    \end{list2}
	
    \section{\mysidestyle Academic Involvement} 

     \begin{list2}
        \item Teaching Assistant  -- Taught 100-level computer science course
        \item ITA Challenge- Was a finalist in ITA’s Programming competition in 2010, 2011.
        \item ACM ICPC - Participated in 2008 USA Competition and placed 18th out of 131 teams.
        \item ACM Student Chapter - Was involved in organization in various capacities (Treasurer, Secretary, SIG-Fun Leader) from 2007-2009.
        \item Linux Users Group: Active member from 2007-2009
        \item Flourish: open source conference:  helped organize and volunteered in 2007.
    \end{list2}


	%
%
    \section{\mysidestyle Academic/Personal Projects } 
     \begin{list2}
        \item Minesweeper and Battleship (Software Design)
        \item EchoBats (Human Computer Interaction)
        \item Simple Interpreter (Object-Oriented Languages)
        \item Simple Message Board (Web Application)

        \item http://www.christinecostales.com/projects
  
    \end{list2}



%\newpage
%% You can use this if you want to add Org Inovlement.
%    \section{\mysidestyle Organizations} 

%     \begin{list2}
%    %    \vspace*{1mm}
%        \item Organization foo -- {\sl 2005-2007 } 
%		\begin{list2}
%		\item Did something interesting
%		\end{list2}
%		\item Organization bar -- {\sl 2006-2007 } 
%		\begin{list2}
%			\item more stuff
%		\end{list2}
%    \end{list2}

%________________________________________________________________________________________
\end{resume}
\end{document}
