% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\newcommand{\addressee}{Human Resources Department } 
\newcommand{\companyName}{Connamara Systems } 
\newcommand{\position}{Software Engineer  }
\newcommand{\companyAddress}{ 200 W. Jackson Blvd., Suite 1340 \\
Chicago, IL 60606 \\
(312) 360-1898  }
\newcommand{\myname}{Christine Costales }

 

\begin{document}

\signature{\myname}                     % name for signature 
\longindentation=0pt                       % needed to get closing flushed left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{\addressee \\
\companyName \\
\companyAddress
 }

\begin{center}
\large\bf CHRISTINE COSTALES\\
555 West Madison Street \#3504 \\ Chicago, IL 60661 \\ Cell: (224) 425-9596
\end{center} 
\vfill % forces letterhead to top of page



\opening{Human Resources:\newline } 


\noindent As a well-rounded computer programmer specializing in Object-Oriented Programming and open source technologies, the position of \position at \companyName peaks my interest. I would relish a chance to contribute to \companyName while developing my C++ skills. Hire me and you’ll get not only a \position with a passion for resolving problems with whichever language or platform it takes, but you’ll also get a nimble skill-set.  \newline


\noindent I've Also been involved in the Linux community in some capacity for the past 10 years, I've started, organized and contributed to Flourish, an open source conference for the past 5 years.  I've also contributed in a small capacity to a several open source projects. \newline 


%\linebreak
\noindent I look forward to speaking with you soon. Pleased find attached copy of my resume. Thank you for your time and consideration.  \newline  \newline  \newline    \newline  



\closing{Sincerely yours,}
%Attachment: Resume
\end{letter}
 

\end{document}
