% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}


\signature{Christine Costales}                     % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{Ms. Import Person \\
Senior Staff Recruiter \\
XYZ Corporation \\
Rt. 56 \\
Anytown, New Jersey 05867} 

\begin{center}
\large\bf CHRISTINE COSTALES  \\
555 West Madison Street \#3504 \\ Chicago, IL 60661 \\ Cell: (224) 425-9596
\end{center} 
\vfill % forces letterhead to top of page


 
\opening{Dear Ms. LastName:} 


	
I would like to express my sincere thanks for giving me the privilege of being interviewed 
for the current position of Application Developer within your company.  Listening to the 
points you have made and from what I read about Publicis Groupe S.A., I am particularly 
impressed with the Company’s performance and its strong commitment to innovation, creativity, 
new technologies implementation and strive for success. I recognize the importance of the 
Application Developer position and I strongly believe that, given the opportunity, I will be 
challenged to perform to my very best in this work environment.

I am confident that my academic training, my computer skills, my desire to learn and my hunger 
for continuous personal improvement utilized in servicing your Company will meet and, I promise, 
exceed your expectations.   

Please, permit me to express my deepest appreciation once more.

I look forward to hearing from you soon.  In the meantime, please contact me if I can provide more information or answer any additional questions.

\closing{Sincerely yours,}
 
 
%\encl{}  				% Enclosures

\end{letter}
 

\end{document}




